Satellite Alignments in the Local Group

### 2017-07-10 paper/paper.tex
sample selection

We build two samples of galaxy pairs. 
The first is a general sample of isolated pairs (IP) and the
second sample correspond to Local Group pairs (LGP).
The halos in these samples only include the DM halos with maximum
circular velocities in the range $ 150\ \kms <V_{\rm max}< 350\ \kms$. We
exclude sub-halos from this selection.

From this set of DM halos we construct the IP sample as follows.
For each halo $A$ we find its closest halo $B$, if halo $A$ is also
the closest to halo $B$, the two halos are considered as a pair. 
Another way to phrase this selection is that pairs do not have
neighbors closer than the pair's distance.
We exclude the pairs that have overlapping virial radii. 
We use this information to exclude all the pairs that have separations
smaller than the sum of their virial radii, i.e. we exclude
We find $49$ pairs with those conditions.

We then count the number of galaxies with $M_V<-9$ inside the virial
radius of each halo, including the central galaxy.
We only keep pairs where both halos have at least 5 bright galaxies, 
reducing the sample to $24$ pairs.  
This is the IP sample.

We build the LGP sample by keeping the pairs in the IP sample with
a separation between its brightest galaxies of $0.75\ \Mpc <R_{AB}< 1.50\ \Mpc$
and a negative relative radial velocity (including the Hubble flow) 
These intervals are close to the Local Group observed values.
The LGP sample is reduced to $12$ pairs.

Figure \ref{fig:samples} show the results for the IP and LGP samples
in the plane of radial velocity versus distance.

@@

>>>>

We build a sample of Local Group Analgues (LGA) by performing a selection on
the stellar mass and isolation properties of the galaxies in the
simulation. The conditions to select LGA galaxies are the following.

\begin{itemize}
\item {\bf Stellar mass}. LGA galaxy pairs are composed by galaxies with stellar mass in the
range $1\times10^{10}\Msun <M_{\star}<1.5 \times 10^{11} \Msun$.
\item {\bf Dominant pairs}. For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
the closest to halo $B$, the two halos are considered as a pair. 
Another way to phrase this selection is that pairs do not have
neighbors closer than the pair's distance.
\item {\bf Separation}. The distance between the galaxies' center of
  mass must be in the range $500$ kpc $<d_{AB}<$ $1500$ kpc. 
\item {\bf Isolation}. For each galaxy in the pair there cannot be a galaxy more
  massive than the lightest galaxy in the pair within a radius of $2$
  Mpc. 
\end{itemize}

We find $19$ pairs of galaxies fulfilling these conditions.
Figure \ref{fig:samples} shows the radial velocity versus distance for
the LGA pairs.

@@

% referencia posiciones satellites
% http://adsabs.harvard.edu/abs/2013MNRAS.435.1928P
